Empirical Analysis of Performance Bottlenecks in Graph Neural Network Training and Inference with GPUs

### 2020-12-26 NEUROC/sec3-experiment-design.tex
更新Section 3.

          Every GNN had a group of hyper-parameters, such as the number of GNN layers and the dimensions of hidden feature vectors.
          %
          The hyper-parameters affected the processing time per epoch and the peak memory usage during training and inference.
          %
          They also affected the accuracy of a GNN.
          %
          Larger hyper-parameter values usually meant more model parameters and more complex models.
          %
          To evaluate their effects, we measured how the training/inference time per epoch, the peak memory usage (of the GPU), and the accuracy on the test set changed as we increased the values of the hyper-parameters.
          %
          Through the experiments, we verified the validity of the time complexity analysis in \tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex}.
          %
          The complexity analysis allowed us to analyze performance bottlenecks theoretically.

    \item[Q2] \emph{Which stage was the most time-consuming stage in GNN training and inference?} (Section~\ref{sec:training_time_breakdown})

          We decomposed the GNN training time on different levels: the layer level, the edge/vertex calculation level, and the basic operator level.
          %
          On each level, we decomposed the training time of an epoch into several stages.
          %
          The most time-consuming stage was the performance bottleneck.
          %
          Optimizing its implementation would significantly reduce the training time.
          %
          For GNN inference, we conducted a similar experimental analysis.
          %
          We discussed the differences in performance characteristics between training and inference.

@@

          The limited memory capacity of a GPU prevented us from training GNNs on big graphs.
          %
          We measured the peak memory usage during GNN training/inference under different graph scales, input feature dimensions, and average degrees.
          %
          Based on the results, we analyzed which was the most memory-consuming component in a GNN.
          %
          Reducing its memory usage would enable us to train GNNs on bigger graphs under the same memory capacity.

    \item[Q4] \emph{Could sampling techniques remove performance bottlenecks in GNN training/inference? Did the use of sampling techniques in training affect model accuracy? } (Section~\ref{sec:effects_of_sampling_techniques_on_performance})

          Theoretically, sampling techniques could significantly reduce the number of graph neurons that participated in the training of a batch.
          %
          Consequently, the processing time and memory usage per batch should also decrease.
          %
          The model accuracy of GNNs might also be affected.
          %
          To validate the effectiveness of sampling techniques, we measured the training/inference time, peak memory usage, and test accuracy under different batch sizes.
          %
          If sampling techniques are effective, they would be the keys to conduct GNN training/inference on very big graphs.
          %
          If they were not effective, we wanted to find out which impaired their efficiency.
          %

>>>>

          Every GNN had a group of hyper-parameters, such as the number of GNN layers and the dimensions of hidden feature vectors.
          %
          The hyper-parameters affected the processing time per epoch and the peak memory usage during training and inference.
          %
          They also affected the accuracy of a GNN.
          %
          Larger hyper-parameter values usually meant more model parameters and more complex models.
          %
          To evaluate their effects, we measured how the training/inference time per epoch, the peak memory usage (of the GPU), and the test accuracy changed as we increased the values of the hyper-parameters.
          %
          Through the experiments, we verified the validity of the time complexity analysis in \tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex}.
          %
          The complexity analysis allowed us to analyze performance bottlenecks theoretically.

    \item[Q2] \emph{Which stage was the most time-consuming stage in GNN training and inference?} (Section~\ref{sec:time_breakdown_analysis})

          We decomposed the GNN training/inference time on different levels: the layer level, the edge/vertex calculation level, and the basic operator level.
          %
          On each level, we decomposed the time of an epoch into several stages.
          %
          The most time-consuming stage was the performance bottleneck.
          %
          Optimizing its implementation would significantly reduce the training time.
          %
          %For GNN inference, we conducted a similar experimental analysis.
          %
          %We discussed the differences in performance characteristics between training and inference.

@@

          The limited memory capacity of a GPU prevented us from conducting training/inference on big graphs.
          %
          We measured the peak memory usage during GNN training/inference under different graph scales, input feature dimensions, and average degrees.
          %
          Based on the results, we analyzed which was the most memory-consuming component in a GNN.
          %
          Reducing its memory usage would enable us to train GNNs on bigger graphs under the same memory capacity.

    \item[Q4] \emph{Could sampling techniques remove performance bottlenecks in GNN training/inference? Did the use of sampling techniques in training sacrifice model accuracy? } (Section~\ref{sec:effects_of_sampling_techniques_on_performance})

          Theoretically, sampling techniques could significantly reduce the number of graph neurons that participated in the training of a batch.
          %
          Consequently, the processing time and memory usage per batch should also decrease.
          %
          The model accuracy of GNNs might also be affected.
          %
          To validate the effectiveness of sampling techniques, we measured the training/inference time, peak memory usage, and test accuracy under different batch sizes.
          %
          If sampling techniques were effective, they would be the keys to conduct GNN training/inference on very big graphs.
          %
          If they were not effective, we wanted to find out which impaired their efficiency.
